\textbf{COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata}

### 2023-04-10 manuscript_v2/main.qmd
changed interlining

---
title: '**COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata**'
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    include-in-header: latex/preamble.sty
    #mainfont: "Palatino Linotype"
    keep-tex: true
linestretch: 2
bibliography: references/refs.bib
csl: references/jama.csl
link-citations: yes #adds links to the citations
---

>>>>

---
title: '**COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata**'
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    include-in-header: latex/preamble.sty
    #mainfont: "Palatino Linotype"
    keep-tex: true
#linestretch: 1
bibliography: references/refs.bib
csl: references/jama.csl
link-citations: yes #adds links to the citations
---

### 2023-04-10 manuscript_v2/main.tex
changed interlining

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, frame hidden, breakable, interior hidden, sharp corners]}{\end{tcolorbox}}\fi

\setstretch{2}
\textsuperscript{1} Centre de Recherches Mathématiques, University of
Montreal, Montréal, Canada\\
\textsuperscript{2} Department of Social and Preventive Medicine, École
de Santé Publique, University of Montreal, Montréal, Canada

>>>>

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi

\textsuperscript{1} Centre de Recherches Mathématiques, University of
Montreal, Montréal, Canada\\
\textsuperscript{2} Department of Social and Preventive Medicine, École
de Santé Publique, University of Montreal, Montréal, Canada
